Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-09 manuscript/manuscript.tex
minor

\section{Real Data Examples}
\label{sec:real}

Using the \textsl{tseries} package \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices. 
It is known as stylized facts that daily return series often exhibts nonlinear
dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
  cont2001empirical}. The Kendall's $\tau$ for the series is
was about $-0.0298$, indicating a fairly weak serial linear correlation, but
certainly not meaning absence of serial dependence.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
with the proposed nonparametric block bootstrap (NPBB) method.
For comparison, we tested the same hypotheses using 1) the
semiparametric bootstrap (SPB) method of \citet{zeimbekakis2022misuses},
which accounts for both serial dependence and unspecified parameters;
2) nonparametric bootstrap (NPB) bias correction method of
\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
The p-values for these tests are summarized in 
Table~\ref{table:SP5004}.

>>>>

\section{A Real Data Example}
\label{sec:real}

Using the \textsl{tseries} package \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices. 
It is known as stylized facts that daily return series often exhibts nonlinear
dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
  cont2001empirical}. The lag-1 Kendall's $\tau$ of the series is
about $-0.0298$, indicating a fairly weak serial linear correlation, but
certainly not meaning absence of serial dependence.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
with the proposed nonparametric block bootstrap (NPBB) method.
For comparison, we tested the same hypotheses using 1) the
semiparametric bootstrap (SPB) method of \citet{zeimbekakis2022misuses},
which accounts for both serial dependence and unspecified parameters;
2) nonparametric bootstrap (NPB) bias correction method of
\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
The p-values for these tests are summarized in 
Table~\ref{table:SP5004}.
